Ignition of Fuel Beds by Firebrands

### 2022-04-04 manuscript4.tex
Updated results for manuscript4

\section{Results and Discussion}
    some text
\section{Conclusions}
    some text

>>>>

\section{Results and Discussion}
    The flaming ignition or non-ignition result of each test is shown in Figure~\ref{fig:multi_heater_hot_vs_ambient}. The markers show the result of each test and the the curves show the logistic regression for each of the heater configurations as defined in Table\ref{tab:multiHeaterConfig} (i.e., tests with the same wind speed, heater spacing, and upstream heater hot or ambient). The shaded regions around the curves represent the 95\% confidence intervals of each regression. The top plot in Figure~\ref{fig:multi_heater_hot_vs_ambient} shows configurations where the downstream heater is actively heated and the upstream heater is at ambient conditions. The bottom plot in Figure~\ref{fig:multi_heater_hot_vs_ambient} shows results for configurations where both heaters are actively heated to the same temperature.
        \begin{figure}[hpbt]
            \centering
            \includegraphics[width=0.75\columnwidth]{Figures/multi_heater_plot.png}
            \caption{Ignition or no ignition outcomes of tests with different heater configurations. The circular markers indicate outcomes of individual tests and the curves represent logistic regressions of each test series. The shaded region shows the 95\% confidence interval for each regression.}
            \label{fig:multi_heater_hot_vs_ambient}
        \end{figure}
    Table~\ref{tab:multiFiftyTemp} shows the heater temperatures estimated to result in a 50\% ignition probability from the logistic regressions shown in Figure~\ref{fig:multi_heater_hot_vs_ambient} with the bounds of the 95\% confidence intervals included. Temperature values for the corresponding wind speed and orientation from the single heater study in Chapter~\ref{part:manuscript2} are shown in the column titled "Single" for comparison. 
        \rowcolors{2}{gray!25}{white}
        \begin{table}[hpbt]
            \normalsize
            \caption{Heater temperature required to achieve 50\% ignition probability for the configurations tested with 95\% confidence intervals shown in parentheses. The single heater column shows the values from the study in Chapter~\ref{part:manuscript2} for a single heater.}
            \centering
            \begin{tabular}{ccrrr}
                \rowcolor{gray!50}
               U\textsubscript{bulk} (\si{\meter\per\second}) & Spacing (D) & Ambient (\si{\celsius})& Heated (\si{\celsius}) & Single (\si{\celsius})\\
                \hline
                0.5  & 1 & 750 (644, 850) & 533 (527, 541) & 571\\
                0.5  & 5 & 578 (565, 583) & 601 (597, 604) & 571\\
                5.8  & 1 & 423 (417, 429) & 406 (397, 416) & 399\\
                5.8  & 5 & 438 (421, 454) & 396 (387, 407) & 399
            \end{tabular}
            \label{tab:multiFiftyTemp}
        \end{table}

    Considering first the cases where both heaters are actively heated there are three observations of note. First, in both the one and five heater diameter spacing cases an increase in wind from 0.5\si{\meter\per\second} to 5.8\si{\meter\per\second} resulted in a lower temperature threshold for ignition. These results are consistent with the results for a single heater presented in Chapter~\ref{part:manuscript2} and are attributed to an increased residence time of pyrolyzates near the heater in recirculation zones enabling ignition at lower temperatures. Second, for the 0.5\si{\meter\per\second} wind speed tests decreasing the heater spacing from five heater diameters to one heater diameter resulted in an 11\% decrease in the temperature required for 50\% ignition probability. The shift in ignition probabilities is attributed to increased heat transfer between the closely spaced heaters. For tests that were conducted with heater temperatures near the 50\% ignition temperature a shift in the model of ignition occurred. For cases where the heaters where spaced five diameters apart ignitions occurred within $\approx$1\si{\second} of the heaters being lowered. Similar ignition times were characteristic of the single diameter spaced heaters at higher temperatures. However, for the single diameter spaced heaters ignitions with heater temperatures near the 50\% ignition limit did not typically ignite until the pyrolysis fronts from both heaters merged. Ignition then occurred in the plume of pyrolyzates between the heaters and anchored to the fuel bed. This phenomena is attributed to .... In contrast to the differences in ignition at a wind speed of 0.5\si{\meter\per\second} the differences in ignition probability were not statistically significant at 5.8\si{\meter\per\second}. This suggests that the enhanced heat transfer between the cartridge heaters is not influential in windy conditions. Anecdotally, in cases under wind ignitions were to occur on the upstream side of the upstream cartridge heater suggesting that ignition is more favorable in the recirculation zones on the upstream side of the heater even with the addition of heat and pyrolysis

    Now considering the cases where the only the upstream heater was actively heated there are three observations of note. Similar to the dual hot and single heater results from Chapter~\ref{part:manuscript2} an increase of wind from

\section{Conclusions}
    some text
